---
title: "Freshwater Mussel Pollution Exposure Report"
author: "Yingpu Guo"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```

```{r source-scripts, include=FALSE}
# Run the project scripts in order.
source(here::here("code", "01_load_data.R"))
source(here::here("code", "02_clean_data.R"))
source(here::here("code", "03_table_summary.R"))
source(here::here("code", "04_figure_pollution.R"))
```

# Introduction

Write a short introduction here about pollution exposure and freshwater mussel health.

# Data

Describe the dataset here. You can mention the source, what each row represents, and the main variables used in the report.

```{r data-preview}
if (exists("raw_data")) {
  utils::head(raw_data)
}
```

# Methods

Describe the workflow here. Explain how the data were loaded, cleaned, summarized, and plotted.

# Results

Add your main table and figure below, then describe what they show.

```{r summary-table}
if (exists("summary_table")) {
  knitr::kable(summary_table, caption = "Starter summary table")
}
```

```{r exploratory-figure, fig.width=7, fig.height=5}
if (exists("pollution_figure")) {
  print(pollution_figure)
}
```

# Discussion

Write your interpretation here. You can also discuss limitations and next steps.
